A new type of automated deduction algorithm based on category theory

### 2022-10-04 aims-template/Template-AIMS Mathematics.tex
switch template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\def\typeofarticle{Type of article}
\def\currentvolume{7}
\def\currentissue{x}
\def\currentyear{2022}
\def\currentmonth{Received date 1 July 2016, Accepted date 6 September}
\def\ppages{xxx--xxx}
\def\DOI{10.3934/math.2022xxx}
\def\Received{July 2021}
\def\Revised{August 2021}
\def\Accepted{September 2021}
\def\Published{December 2021}

@@

\maketitle

\section{Introduction}

Please use the AIMS template to prepare your manuscript, 
before you submit to our journal. 
Please read carefully the instructions for authors at
http://www.aimspress.com \cite{authour1}. 
These are important instructions and explanations. 
Thank you for your cooperation.

\section{Materials and methods}
\subsection{Subheading}

\subsubsection{Sub-subheading}
The heading levels should not be more than 4 levels. 
The font of heading and subheadings should be 12 point 
normal Times New Roman. The first letter of headings 
and subheadings should be capitalized.

\section{Results}
The body text is in 12 point normal Times New Roman, 
the line space is at least 15 point.

\begin{table}[H]
\begin{center}
\caption{Caption of the table.}
\begin{tabular}{ccc} \hline
 & & \\\hline
 & & \\
 & & \\
 & & \\\hline
 &(Table body should be created by MS word table function; three-line table is preferred.)
\end{tabular}
\end{center}
\end{table}

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.8]{figure.pdf}
\caption{Legend of the figure.}
\label{Fig1}
\end{center}
\end{figure}

\begin{equation}
  \text{[add an equation here; use MS Word or MathType equation function]}
\end{equation}

\section{Discussion}

\section{Conclusions}

\section*{Acknowledgments (All sources of funding of the study must be disclosed)}
We would like to thank you for following the instructions above 
very closely in advance. It will definitely save us lot of 
time and expedite the process of your paper's publication.

\section*{Conflict of interest}

\begin{thebibliography}{999}

\bibitem{authour1}[10.1090/S0894-0347-1992-1124979-1]
      \textbf{Journal article style:} Y. Benoist, P. Foulon, F. Labourie,  {Anosov flows with stable and unstable differentiable distributions},
     \newblock  {\it J. Amer. Math. Soc.,}
     \newblock  \textbf{Volume} (year), StaringPage-Ending Page. \doilink{http://dx.doi.org/10.1090/S0894-0347-1992-1124979-1}

\bibitem{authour2}[10.1016/B978-0-12-775850-3.50017-0]
     \textbf{Book style:}
    \newblock J. Serrin, {\em Gradient estimates for solutions of nonlinear elliptic and parabolic equations}, 
    \newblock  2 Eds., New York: Academic Press, 1971. \doilink{http://dx.doi.org/10.1016/B978-0-12-775850-3.50017-0}

\bibitem{authour3}
     \textbf{Online content:}
    \newblock  {\it SARS Expert Committee, SARS in Hong Kong: From Experience to Action}, Hong Kong SARS Expert Committee, 2003. Available from: \\ \url{http://www.sars-expertcom.gov.hk/english/reports/reports.html.}

\end{thebibliography}

For more questions regarding reference style, please refer to the \href{http://www.ncbi.nlm.nih.gov/books/NBK7256/}{Citing Medicine}.

\section*{Supplementary (if necessary)}

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts,verbatim}

@@

\maketitle
\end{document}

### 2022-10-04 aims-template/paper.new.tex
switch template

\documentclass[preprint]{elsarticle}

\hfuzz=2pt
%% \special{dvipdfmx:config z 0} %% speed boost

%% The commands below, learnt from TeX stack exchange can cancel the hbox overfull warning...
\usepackage{etoolbox}
\makeatletter
\patchcmd\ps@pprintTitle
{\fi\fi\fi\fi}
{\fi\fi\fi\fi
	\afterassignment\fix@elsarticle\let\@tempa}
{}{\FailedToPatch}
\def\fix@elsarticle{\iffalse{\fi}\romannumeral-`0}
\makeatother

%% \usepackage[letterpaper, total={5.3in, 9in}]{geometry}	%% set paper size & margin
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution
\usepackage{setspace}	%% double spacing

@@

\newtheorem{theorem}{Theorem}	%% definition for theorem env
\newtheorem{axiom}{Axiom}	%% definition for axiom env
\newdefinition{definition}{Definition}	%% definition for definition env

@@

%% \setlength{\parskip}{0.8em}	%% set white space between paragraphs

\doublespacing

\begin{document}

\begin{frontmatter}
	\title{A new type of automated prover based on category theory}

	\author[1]{Shao Xinhui\corref{cor1}}
	\ead{shaoxinhui@mail.neu.edu.cn}

	\author[2]{Zijian Wang\fnref{fn2}}
	\ead{felix_wzj@yahoo.com}
	\ead[url]{zijianfelixwang.github.io}

	\cortext[cor1]{Corresponding author, guiding the first author through the process of the research, professor of the Northerneastern University.}

	\fntext[fn2]{Author conducting the research, student of the Northeast Yucai School of P.R.China}

	\affiliation[1]{organization={Department of Mathematics, College of Sciences, Northerneastern University},city={Shenyang},postcode={110000},addressline={Department of Mathematics, College of Sciences, Northerneastern University},country={P.R.China}}
	\affiliation[2]{organization={Northeast Yucai School},addressline={Zhenxing St. 9-5, Heping District},city={Shenyang},postcode={110000},country={P.R.China}}
	%% \maketitle

	\begin{abstract}
	In this article a new type of automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets provide an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given. The AMS codes are 03B35, 68V15, 18-00, 18-04, 68W99.
	\end{abstract}

	\begin{graphicalabstract}
		\begin{figure}[h]
			\begin{tikzpicture}[commutative diagrams/every diagram]
				\node (K0) at (90:2.3cm) {$\mathcal{K}_0$};
				\node (K1) at (90+72:2cm) {$\mathcal{K}_1$};
				\node (K2) at (90+2*72:2cm) {$\mathcal{K}_2$};
				\node (K3) at (90+3*72:2cm) {$\mathcal{K}_3$};
				\node (Kn) at (90+4*72:2cm) {$\mathcal{K}_N$};

				\path[commutative diagrams/.cd, every arrow, every label, dashed]
				(K3) edge node {$K_3$} (Kn)
				(Kn) edge node {} (K1)
				(Kn) edge node {$k_N$} (K0);
			\end{tikzpicture}
		\end{figure}
	\end{graphicalabstract}

	\begin{keyword}
		automatic prover \sep theorem prover \sep algorithm \sep category theory \sep automatic deduction \sep automatic reasoning
	\end{keyword}
\end{frontmatter}

@@

When we humans think of mathematical problems and perform proofs, we do not follow purely logical ways like complex stuff like Cooper{'}s algorithm. Instead, we just perform tries to seek breakthrough points using his knowledge in a diversified thought. Why cannot programs do things like that? Why can not they perform some sort of knowledge transferring? Carry this question and in experimental and curious attitude, I conducted the research on this topic and have found a utility to do the task: the category theory.

@@

In this paper I will present a new approach of automated proving using knowledge of the category, as well as its theoretical foundation, and will provide a new algorithm which can prove mathematical statements comprehensively. Additionally, an executable program and its implementation process will be described later.

\textit{ Structure of the paper.}\\
The paper mainly consists of seven sections. The Introduction section demonstrates the background of the research and fundamental opinions around it. The Preliminaries section, made up of two subsections, claims to minimized pre-knowledge required to understand the paper and the symbols I select to use. The third section defines a set of mathematical structures that will be used by the algorithm. The forth section explains the detailed workflow procedures of the algorithm. The next section claims the conclusions of the research and the to-do improvements in the future. Finally the Acknowledgments section expresses my gratitude to the help and the References section claims the referential resources used while conducting the project.

@@

The definition below describes how the recursive functor uses the knowledge base and the further evolution for the data structure of the knowledge base. It ought to be paid attention to that although in the Introduction part that I say this new method of implementing a prover makes the prover low-knowledge and it turns out to have an infrastructure called the knowledge base. This is not conflictual since the knowledge I mean by in the Introduction section means the algorithm is automated, which means it does not require users to give in too much assistance and it does not know exactly what is under manipulation. On the other hand, however, the knowledge word here means by the storage of reflections, which can be rules, axioms, theorems, lemmas and even strategies.

@@

	It is easy to understand that for each reflection functor \(\mathcal{K}_a\) and \(\mathcal{K}_b\), the count of set \(\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_a,\mathcal{K}_b\right)\) indicates the \textbf{ weight} of \(\mathcal{K}_b\) to \(\mathcal{K}_a\), controlling the probability of \(\mathcal{K}_b\) to be selected when the former functor is \(\mathcal{K}_a\). The design of this process is inspired by the lottery scheduling algorithm I learned in Andrew S. Tanenbaum{'}s Operating Systems: Design and Implementation \cite{Tanenbaum2015} before.
\end{definition}

@@

In the sections before I have presented an elegant data structure for representing mathematical concepts and a neat process which utilizes category theory concepts and knowledge to conduct proof, which also have self-optimiza-tion features.

Currently I have developed a computer program called DefQed that implements the algorithm and it is open-sourced with BSD 3-Clause {``}New{''} or {``}Revised{''} License on GitHub. The source code of the latest version can be accessed at \cite{Wang2022} It should be noted that the version is very early and some aspects of the algorithm I presented in the paper is not implemented.

Future works are the followings below:
\begin{itemize}
	\item \textbf{Continuing the implementation of the corresponding software.} Currently the software I developed is still under immature development and a great many of the aspects I presented in the paper above, including the self-evolution logic, have not been constructed yet.
	\item  \textbf{Improving the algorithm.} The algorithm I presented in the paper is not mature. For instance, if the knowledge base has more than \(2^{32}\) morphisms, then some of the morphisms will never be utilized.
	\item \textbf{Optimizing the algorithm.} Currently, though the design of the procedures increase generality because of the low-knowledge feature, the performance of derivations may be lower than the current algorithms, which focus on a certain subject inside mathematics.
\end{itemize}

@@

\bibliographystyle{elsarticle-num}
\bibliography{paper}

\end{document}

>>>>

\documentclass{aims}

%% \special{dvipdfmx:config z 0} %% speed boost
\usepackage{txfonts, verbatim}
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution
\usepackage{setspace}	%% double spacing
\usepackage{url}	%% for reference 9
\usepackage[pagewise]{lineno}\linenumbers

@@

\def\typeofarticle{}
\def\currentvolume{}
\def\currentissue{}
\def\currentyear{}
\def\currentmonth{}
\def\ppages{}
\def\DOI{}
\def\Received{}
\def\Revised{}
\def\Accepted{}
\def\Published{}

\numberwithin{equation}{section}
\DeclareMathOperator*{\essinf}{ess\,inf}
\makeatletter
\renewcommand{\@biblabel}[1]{#1\hfill \hspace{-0.2cm}}
\makeatother

\newcommand{\ep}{\varepsilon}
\newcommand{\eps}[1]{{#1}_{\varepsilon}}

\newtheorem{theorem}{Theorem}	%% definition for theorem env
\newtheorem{axiom}{Axiom}	%% definition for axiom env
\newtheorem{definition}{Definition}	%% definition for definition env

@@

\begin{document}
	\title{A new type of generalized, self-evolving and efficient automated deduction algorithm based on category theory}
	\author{%
		Shao Xinhui\affil{1}\corrauth
		Zijian Wang\affil{2}
	}
	\shortauthors{the Authors}
	\address{%
		\addr{\affilnum{1}}{Department of Mathematics, College of Sciences, Northerneastern University, Shenyang, Liaoning, P.R.China}
		\addr{\affilnum{2}}{Northeast Yucai School, Zhenxing St. 9-5, Heping District, Shenyang, Liaoning, P.R.China}
		\corraddr{shaoxinhui@mail.neu.edu.cn}
	}

	\begin{abstract}
	In this article a new type of automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets provide an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given.
	\end{abstract}

	\keywords{
		\textbf{automatic prover, theorem prover, algorithm, category theory, automatic deduction, automatic reasoning}
		\newline
		\textbf{Mathematics Subject Classification:} 03B35, 68V15, 18-00, 18-04, 68W99
	}

	\maketitle

@@

	When we humans think of mathematical problems and perform proofs, we do not follow purely logical ways like complex stuff like Cooper{'}s algorithm. Instead, we just perform tries to seek breakthrough points using his knowledge in a diversified thought. Why cannot programs do things like that? Why can not they perform some sort of knowledge transferring? Carry this question and in experimental and curious attitude, we conducted the research on this topic and have found a utility to do the task: the category theory.

@@

	In this paper we will present a new approach of automated proving using knowledge of the category, as well as its theoretical foundation, and will provide a new algorithm which can prove mathematical statements comprehensively. Additionally, an executable program and its implementation process will be described later.

	\textit{ Structure of the paper.}\\
	The paper mainly consists of seven sections. The Introduction section demonstrates the background of the research and fundamental opinions around it. The Preliminaries section, made up of two subsections, claims to minimized pre-knowledge required to understand the paper and the symbols we select to use. The third section defines a set of mathematical structures that will be used by the algorithm. The forth section explains the detailed workflow procedures of the algorithm. The next section claims the conclusions of the research and the to-do improvements in the future. Finally the Acknowledgments section expresses my gratitude to the help and the References section claims the referential resources used while conducting the project.

@@

	The definition below describes how the recursive functor uses the knowledge base and the further evolution for the data structure of the knowledge base. It ought to be paid attention to that although in the Introduction part that we say this new method of implementing a prover makes the deduction algorithm low-knowledge and it turns out to have an infrastructure called the knowledge base. This is not conflictual since the knowledge we mean by in the Introduction section means the algorithm is automated, which means it does not require users to give in too much assistance and it does not know exactly what is under manipulation. On the other hand, however, the knowledge word here means by the storage of reflections, which can be rules, axioms, theorems, lemmas and even strategies.

@@

		It is easy to understand that for each reflection functor \(\mathcal{K}_a\) and \(\mathcal{K}_b\), the count of set \(\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_a,\mathcal{K}_b\right)\) indicates the \textbf{ weight} of \(\mathcal{K}_b\) to \(\mathcal{K}_a\), controlling the probability of \(\mathcal{K}_b\) to be selected when the former functor is \(\mathcal{K}_a\). The design of this process is inspired by the lottery scheduling algorithm we learned in Andrew S. Tanenbaum{'}s Operating Systems: Design and Implementation \cite{Tanenbaum2015} before.
	\end{definition}

@@

	In the sections before we have presented an elegant data structure for representing mathematical concepts and a neat process which utilizes category theory concepts and knowledge to conduct proof, which also have self-optimiza-tion features.

	Currently we have developed a computer program called DefQed that implements the algorithm and it is open-sourced with BSD 3-Clause {``}New{''} or {``}Revised{''} License on GitHub. The source code of the latest version can be accessed at \cite{Wang2022} It should be noted that the version is very early and some aspects of the algorithm we presented in the paper is not implemented.

	Future works are the followings below:
	\begin{itemize}
		\item \textbf{Continuing the implementation of the corresponding software.} Currently the software we developed is still under immature development and a great many of the aspects we presented in the paper above, including the self-evolution logic, have not been constructed yet.
		\item  \textbf{Improving the algorithm.} The algorithm we presented in the paper is not mature. For instance, if the knowledge base has more than \(2^{32}\) morphisms, then some of the morphisms will never be utilized.
		\item \textbf{Optimizing the algorithm.} Currently, though the design of the procedures increase generality because of the low-knowledge feature, the performance of derivations may be lower than the current algorithms, which focus on a certain subject inside mathematics.
	\end{itemize}

@@

	\section*{Conflict of interests}
	This research did not receive any specific grant from funding agencies in the public, commercial, or
	not-for-profit sectors.

	\bibliographystyle{plain}
	\bibliography{paper}
\end{document}

### 2022-10-04 paper.new.tex
switch template

\usetikzlibrary{positioning, cd, arrows}	%% for comutative diagram & flowchart drawing

@@

@@

	\begin{abstract}
	In this article a new type of automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets provide an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given.
	\end{abstract}

@@

	\textit{ Structure of the paper.}\\
	The paper mainly consists of seven sections. The Introduction section demonstrates the background of the research and fundamental opinions around it. The Preliminaries section, made up of two subsections, claims to minimized pre-knowledge required to understand the paper and the symbols we select to use. The third section defines a set of mathematical structures that will be used by the algorithm. The forth section explains the detailed workflow procedures of the algorithm. The next section claims the conclusions of the research and the to-do improvements in the future. Finally the Acknowledgments section expresses my gratitude to the help and the References section claims the referential resources used while conducting the project.

@@

	\begin{table}
		\centering
		\label{table-1}
		\caption{The table for $\mathit{p}(\mathcal{N})$}
		\begin{tabular}{ccccccccccc}
			\toprule
			$\mathcal{N}$ & int & num & inf & $\sum$ & $=$ & $/$ & - & abs & $<$ & for \\
			\midrule
			$\mathit{p}$ & $0$ & $0$ & $0$ & $3$ & $2$ & $2$ & $2$ & $1$ & $2$ & $2$ \\
			\bottomrule
		\end{tabular}
	\end{table}

@@

		\begin{figure}[ht]
			\centering
			\begin{tikzpicture}[commutative diagrams/every diagram]
				\node (K0) at (90:2.3cm) {$\mathcal{K}_0$};
				\node (K1) at (90+72:2cm) {$\mathcal{K}_1$};
				\node (K2) at (90+2*72:2cm) {$\mathcal{K}_2$};
				\node (K3) at (90+3*72:2cm) {$\mathcal{K}_3$};
				\node (Kn) at (90+4*72:2cm) {$\mathcal{K}_N$};

@@

	\begin{figure}[h!t]
		\centering
		\begin{tikzpicture}[>=latex', font={\sf \small}]
			\def\smbwd{1cm}

>>>>

\usetikzlibrary{positioning, cd, arrows, celtic}	%% for comutative diagram & flowchart drawing

@@

%\pdfminorversion=7

@@

	\begin{abstract}
	In this article a new type of generalized, self-evolving and efficient automated statement proof algorithm based on new data structures, i.e. brackets and map graphs
	and new algorithms is presented. The brackets structure provides an elegant low-knowledge representation of mathematical concepts. The map graphs offer an efficient machine-learning method which let the computer learn knowledge while proving. Additionally, the new finding is totally built on the category theory. Furthermore, a prototype of the program is given and examined for performance.
	\end{abstract}

@@

	\textit{ Structure of the paper.}\newline
	The paper mainly consists of seven sections. The Introduction section demonstrates the background of the research and fundamental opinions around it. The Preliminaries section, made up of two subsections, claims to minimized pre-knowledge required to understand the paper and the symbols we select to use. The third section defines a set of mathematical structures that will be used by the algorithm. The forth section explains the detailed workflow procedures of the algorithm. The next section claims the conclusions of the research and the to-do improvements in the future. Finally the Acknowledgments section expresses my gratitude to the help and the References section claims the referential resources used while conducting the project.

@@

	\begin{table}[h]
		\centering
		\caption{The table for $\mathit{p}(\mathcal{N})$}
		\begin{tabular}{ccccccccccc}
			\toprule
			$\mathcal{N}$ & int & num & inf & $\sum$ & $=$ & $/$ & - & abs & $<$ & for \\
			\midrule
			$\mathit{p}$ & $0$ & $0$ & $0$ & $3$ & $2$ & $2$ & $2$ & $1$ & $2$ & $2$ \\
			\bottomrule
		\end{tabular}
		\label{table-1}
	\end{table}

@@

		\begin{figure}[h]
			\centering
			\begin{tikzpicture}[commutative diagrams/every diagram]
				\node (K0) at (90:2.3cm) {$\mathcal{K}_0$};
				\node (K1) at (90+72:2cm) {$\mathcal{K}_1$};
				\node (K2) at (90+2*72:2cm) {$\mathcal{K}_2$};
				\node (K3) at (90+3*72:2cm) {$\mathcal{K}_3$};
				\node (Kn) at (90+4*72:2cm) {$\mathcal{K}_N$};

@@

	\begin{figure}[h]
		\centering
		\begin{tikzpicture}[>=latex', font={\sf \small}]
			\def\smbwd{1cm}

### 2022-10-04 paper.tex
switch template

\documentclass[preprint]{elsarticle}

\hfuzz=2pt
%% \special{dvipdfmx:config z 0} %% speed boost

%% The commands below, learnt from TeX stack exchange can cancel the hbox overfull warning...
\usepackage{etoolbox}
\makeatletter
\patchcmd\ps@pprintTitle
{\fi\fi\fi\fi}
{\fi\fi\fi\fi
	\afterassignment\fix@elsarticle\let\@tempa}
{}{\FailedToPatch}
\def\fix@elsarticle{\iffalse{\fi}\romannumeral-`0}
\makeatother

%% \usepackage[letterpaper, total={5.3in, 9in}]{geometry}	%% set paper size & margin
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution
\usepackage{setspace}	%% double spacing

@@

\newtheorem{theorem}{Theorem}	%% definition for theorem env
\newtheorem{axiom}{Axiom}	%% definition for axiom env
\newdefinition{definition}{Definition}	%% definition for definition env

@@

\begin{frontmatter}
	\title{A new type of automated prover based on category theory}

@@

	\affiliation[1]{organization={Department of Mathematics, College of Sciences, Northerneastern University},city={Shenyang},postcode={110000},addressline={Department of Mathematics, College of Sciences, Northerneastern University},country={P.R.China}}
	\affiliation[2]{organization={Northeast Yucai School},addressline={Zhenxing St. 9-5, Heping District},city={Shenyang},postcode={110000},country={P.R.China}}
	%% \maketitle

@@

Additionally, I had few knowledge about \LaTeX before writing this paper. The $lshort$ documentation and the \TeX Stack Exchange helped me a lot. Here I express my genuine thankfulness to the online resources and documentation of the used \LaTeX packages and software components.

>>>>

\documentclass{aims}

%% \special{dvipdfmx:config z 0} %% speed boost

%% \usepackage[letterpaper, total={5.3in, 9in}]{geometry}	%% set paper size & margin
\usepackage{amsmath}	%% math part 1
\usepackage{flexisym, breqn}	%% math part 2
\usepackage{amssymb, graphics, setspace}	%% math part 3
\usepackage{tikz, tikz-cd}	%% for commutative diagrams
\usepackage{flowchart}	%% for flowchart
\usepackage{float, booktabs}	%% for table & alignment
\usepackage{algorithmicx, algorithm, algpseudocode}	%% for pseudo code composition
\usepackage{blindtext}	%% overfull hbox solution
\usepackage{setspace}	%% double spacing
\usepackage{url}	%% for reference 9

@@

\newtheorem{theorem}{Theorem}	%% definition for theorem env
\newtheorem{axiom}{Axiom}	%% definition for axiom env
\newtheorem{definition}{Definition}	%% definition for definition env

@@

\begin{frontmatter}
	\title{A new type of automated deduction algorithm based on category theory}

@@

	\affiliation[1]{organization={Department of Mathematics, College of Sciences, Northerneastern University},city={Shenyang},postcode={110000},addressline={Department of Mathematics, College of Sciences, Northerneastern University},country={P.R.China}}
	\affiliation[2]{organization={Northeast Yucai School},addressline={},city={Shenyang},postcode={110000},country={P.R.China}}
	%% \maketitle

@@

Additionally, I had few knowledge about \LaTeX before writing this paper. The $lshort$ documentation and the \TeX Stack Exchange helped me a lot. Here I express my genuine thankfulness to the online resources and documentation of the used \LaTeX packages and software components. This research did not receive any specific grant from funding agencies in the public, commercial, or
not-for-profit sectors.
